Measurement of deeply virtual Compton scattering off Helium-4

### 2020-02-13 eg6-letters/long-paper/prc-dvcshelium.tex
Several minor edits, fix compile

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{lineno}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}

@@

@@

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$ of the 
spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
%\small
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
%\normalsize
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor \cite{Belitsky:2008bz} and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$. 
%Their explicit expressions can be found in Appendix 
%\ref{app:Helium_cross_section}.

The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
the $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
$\alpha$ coefficient is known and characteristic, such that a fit is easy. The only caveat
is the large difference of magnitude between the $\alpha$ factors, which will lead to 
rather different error propagation for the two parts of the CFF.

@@

@@

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed in Chap. \ref{chap:pheno}. Two important differences in the 
reaction need to be accounted however, the different initial state and the addition of 
final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
target are possible, including possible charge exchange. The latter
leading to contamination from other channels, in particular charge exchange can lead to
large differences in this background.

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Since, modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf}, we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging to control them. This process
and how it can help with these issues will be discussed
in details at the end of the present chapter.

\subsection{The HERMES nuclear DVCS measurements}

The first measurement of nuclear DVCS has been performed by the HERMES collaboration 
\cite{Airapetian:2009cga}.
This experiment covered an array of nuclear target and looked at the $A$ dependence of the
BSA signal. The results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large error bars, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about the nuclear effect. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

@@

An issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
challenging this assumption and could explain the tension between theory and experiment.

@@

The CLAS experiment had for main objective to explore the coherent DVCS on helium-4 and assess if
the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
perform this measurement however, several instrumentation challenges need to be passed. First, to
measure the scattered electron and the low angle photon of the DVCS, for which we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a solenoid magnet. Second, the
helium recoil need to be measured to ensure the exclusivity of the reaction. In this section, we 
will rapidly describe the particular detector setup used in our experiment.

@@

CLAS is installed in the hall B of the JLab main accelerator. It has for main objective to study the 
multi-particles final states
that cannot be reconstructed with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement.

The CLAS spectrometer \cite{Mecking:2003zu} is composed of six identical radial 
sectors separated by a toroidal magnet and each sector is made of four detectors 
as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
are placed in the solenoid area to reconstruct the charge particle's tracks and 
calculate their momentum. Then, an array of scintillators is placed to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
This is completed by two important forward detectors, from 8 
to 45 degrees for electron identification, a Cerenkov counter 
\cite{Adams:2001kk} and an electromagnetic calorimeter \cite{Amarian:2001zs}.

@@

The inner calorimeter, illustrated in Fig. \ref{fig:IC} is a homogeneous 
calorimeter composed 424 lead tungstate 
(PbWO) crystals read out by $5 \times 5$ mm$^2$ avalanche photo-diodes (APDs). 
It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
particularly sensitive to the Moller electrons scattered at low angles.

@@

The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
and 200 MeV/c at our beam energy. Therefore, a specific detector was 
needed to detect them. To design the present setup, large inspiration was drawn from the 
Bonus setup that also used a GEM based RTPC \cite{Fenker:2008zz}, installed in CLAS to 
detect slow protons out of a deuterium target \cite{Baillie:2011za}. In such an RTPC the 
charges are projected toward large radii 
rather than towards the endcaps, as is more traditional in time 
projection chambers. This design allows to reduce significantly the drift time and reduce the 
amount of pile-up from accidental events. The RTPC has been described in more 
details elsewhere \cite{Dupre:2017upj}, here is a summary of key elements.

@@

The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
of the electron and the large signal in both the Cerenkov counter and electromagnetic calorimeter
provide the identification. A signal of good quality is also required in the 
time-of-flight system, which serves as a time reference for other detectors. In particular, it 
serves for the identification of the protons, which is based on a 
time-of-flight measurement. Several 
fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
go up to 10\% at the detection limit of 200 MeV/c.

@@

The second important source of background comes from accidentals. Despite the many exclusivity cuts, it is 
possible to have particles from different events getting combining and pass all the cuts and get 
into the data sample. To evaluate the number of such events, we invert the vertex selection 
of the two charged 
particles of the process, electron and helium (or proton in the incoherent case), and request that they
are separate. We find 4.1\% of the coherent and 6.5\% of the incoherent samples are accidentals.

@@

As discussed above, the best way to define $t$ in the incoherent channel is not completely
straightforward. As can be seen in the Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between them by analyzing the data independently using the two 
definitions. We found no significant difference between them, as is 
illustrated in Fig. \ref{fig:ttpComp}. We use in our final results $t$,
which is the correct definition.

@@

In order to compare to models, we extract the BSA at 90° in Fig. \ref{fig:CohALU90}. The model 
compared to the data \cite{Liuti:2005gi} is based on the idea that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei with a nuclear
spectral function. It appears that the model undershoot our results systematically. However, 
a more recent calculation, using similar principles but with a more advanced nuclear spectral 
function \cite{Fucini:2018gso} has been able to reproduce the data very well. This 
sort of theoretical model, also able to describe the EMC effect, is the only one which has 
been confronted to this data yet. We observe that reproducing these data is not 
straightforward and necessitates an advanced nuclear model.

@@

\begin{acknowledgments}
 Put your acknowledgments here.
\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{basename of .bib file}

>>>>

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{lineno}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developpements with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies can be generalized to the
nucleus and offer a unique opportunity to revisit the quark structure of the nucleus
with an original perspective. This new approach is particularly needed as the quark
structure of the nucleus remains today the subject of numerous
controvercies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions (PDFs), the observed shape of the PDF ratio, known as
EMC effect, remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the generalized parton distributions (GPDs) can be probed conveniently through
spin assymetries in the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. Indeed, the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium. Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
is significantly simplified with the reduction to a single GPD intervening in the process. The 
measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
the HERMES collaboration \cite{Airapetian:2009cga} lead to imprecise results. We present here
more recent and detailed measurements from the CLAS collaboration already partially presented
in previous letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the nuclear DVCS CLAS experiment, detail the methods used for the
data analysis and produce the full experimental results for each channel measured.

@@

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$ of the 
spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
%\small
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
%\normalsize
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.

%Their explicit expressions can be found in Appendix 
%\ref{app:Helium_cross_section}.

The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
the $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
$\alpha$ coefficient has a characteristic $\phi$ dependence, such that a fit can
easily separate their respective contributions. The only caveat
is the large difference of magnitude between the $\alpha$ factors, which can lead to 
rather different error propagation for the two parts of the CFF.

@@

An important issue with the use of this theoretical framework is the large mass of the 
helium nuclei. In principle, this could lead to significant target mass corrections...
REF? \cite{Braun:2012bg}

@@

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed many times in the litterature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
Two important differences need to be accounted for however, the different initial state and the addition of 
final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
target are possible, including possible charge exchange. The latter
leading to contamination from other channels, in particular charge exchange can lead to
a large contribution from such background reaction.

@@

Since, DVCS is a 
process selected using tight exclusivity constrains, some of the initial and final-state effects are
automatically mitigated. Selection criterion on missing energy and momentum are performed,
constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
calculation is available to correct for the reminder of these effects yet. Since, modern calculations exist 
for such effects in DIS \cite{Cosyn:2017ekf}, we can expect them to be extended to the DVCS 
process as more data becomes available. Another avenue of progress
on this topic will be the use of experimental techniques like tagging. This process
can help to control both initial and final state effects by detecting the nuclear remnant.
In the tagged process the target breaks in two providing directly the initial state
of the struck nucleon, while a measured backward nuclear fragment limits significantly the
impact of final state effects.

\section{Past nuclear DVCS measurements}

The first measurement of nuclear DVCS has been performed by the HERMES collaboration 
\cite{Airapetian:2009cga}.
This experiment covered an array of nuclear target and looked at the $A$ dependence of the
BSA signal. Thier results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large error bars, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about any nuclear effect. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

@@

An important issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution may not be good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
challenging this assumption and could explain the tension between theory and experiment.

@@

The CLAS experiment had for main objective to explore the coherent DVCS on helium-4 and assess if
the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
perform this measurement however, several instrumentation challenges need to be passed. First, to
measure the scattered electron and the low angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a solenoid magnet. Second, the
helium recoil need to be measured to ensure the exclusivity in the coherent channel. In this section, we 
will rapidly describe the particular detector setup used in our experiment.

@@

The CLAS spectrometer \cite{Mecking:2003zu} is installed in the hall-B of the JLab main 
accelerator. It has for main objective to study the multi-particles final states
that cannot be reconstructed with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement.  
CLAS is composed of six identical radial 
sectors separated by a toroidal magnet and each sector is made of four detectors 
as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
are placed in the solenoid area to reconstruct the charge particle's tracks and 
calculate their momentum. Then, an array of scintillators is placed to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
This is completed by two important forward detectors, from 8 
to 45 degrees for electron identification, a Cerenkov counter 
\cite{Adams:2001kk} and an electromagnetic calorimeter \cite{Amarian:2001zs}.

@@

The inner calorimeter, illustrated in Fig. \ref{fig:IC} is a homogeneous 
calorimeter composed 424 lead tungstate 
(PbWO) crystals read out by $5 \times 5$ mm$^2$ avalanche photo-diodes (APDs). 
It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
particularly sensitive to the Moller electrons scattered from the target at small angles.

@@

The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
and 200 MeV/c at our beam energy. Therefore, a specific detector was 
needed to detect them. To design the present setup, large inspiration was drawn from the 
Bonus setup that also used a GEM based RTPC \cite{Fenker:2008zz}, installed in CLAS to 
detect slow protons out of a deuterium target \cite{Baillie:2011za}. In such an RTPC the 
charges are projected toward large radii 
rather than towards the endcaps, as is more traditional in time 
projection chambers. This design allows to reduce significantly the drift time and reduce the 
amount of pile-up from accidental events. The RTPC design, its operation, calibration and 
the track reconstruction have been described in more 
details elsewhere \cite{Dupre:2017upj}, here is a summary of key elements.

@@

The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
of the electron and the large signal in both the Cerenkov counter and electromagnetic calorimeter
provide the identification. A signal of good quality is also required in the 
time-of-flight system, which serves as a time reference for other detectors. In particular, it 
serves for the identification of the protons. Several 
fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
go up to 10\% at the detection limit of 200 MeV/c.

@@

The second important source of background comes from accidentals. Despite the many exclusivity cuts, it is 
possible to have particles from different events getting combined and pass all the cuts and get 
into the data sample. To evaluate the number of such events, we invert the vertex selection 
of the two charged 
particles of the process, electron and helium (or proton in the incoherent case), and request that they
are separate. We find 4.1\% of the coherent and 6.5\% of the incoherent samples are accidentals.

@@

As discussed above, the best way to define $t$ in the incoherent channel is not completely
straightforward. As can be seen in the Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between them by analyzing the data independently using the two 
definitions. We found no significant difference between them, as is 
illustrated in Fig. \ref{fig:ttpComp}. We use in our final results $t$,
which is the correct definition with the slightly poorer resolution.

@@

We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model 
compared to the data \cite{Liuti:2005gi} is based on the idea that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei with a nuclear
spectral function. It appears that the model undershoot our results systematically. However, 
a more recent calculation, using similar principles but with a more advanced nuclear spectral 
function \cite{Fucini:2018gso} has been able to reproduce the data very well. This 
sort of theoretical model, also able to describe the EMC effect, is the only one which has 
been confronted to this data yet. We observe that reproducing these data is not 
straightforward and necessitates an advanced nuclear model.

@@

\begin{acknowledgments}
	% Add Sergio and ERC!
 Put your acknowledgments here.
\end{acknowledgments}

\appendix
\section{Detailed equations}
\label{sec:eq}
 tests

% Create the reference section using BibTeX:
\bibliography{hadro.bib}
